Conex - establishing trust into data repositories

### 2016-06-09 paper.tex
Just a few minor remarks

Opam 2.0 is not released yet, but fixes major concerns:
downloading validates the TLS certificates~\cite{opampr} using system-wide trust anchors,
a wrap command is available for building and installing packages~\cite{wrappr}.
Nevertheless, a breach of the central server enables an attacker to modify packages arbitrarily.
Relying only on TLS for packages is suboptimal, because many TLS implementations suffer from a long history of security vulnerabilities (e.g. goto fail).

@@

@@

Each author updates their own packages, which should be free of conflicts due to separate resources for each package.
If a conflict is detected, it is up to the janitors to decide which update should go through, and which should be resubmitted on top of the other.

@@

The \texttt{keys} directory contains one file for each author, named after the key identifier.
The \texttt{sigs} directory contains one file for each janitor, named after the janitor key identifier.
The \texttt{data} directory consists of subdirectories, which each must contain a file \texttt{authorisation} and a file \texttt{releases}, plus possibly any subdirectories.
Each subdirectory must be listed in the \texttt{releases} file, and must contain a \texttt{checksum} file besides any other data files and directories (all listed in the checksum file).

@@

Package metadata, signatures, and public keys are distributed in the same repository to prevent attackers from hindering one communication link, e.g. the public key one.
This would otherwise allow a detected attacker who compromised a key to deliver metadata signed with this compromised key.

>>>>

Opam 2.0 is not released yet, but fixes major concerns:
downloading validates the TLS certificates~\cite{opampr} using system-wide trust anchors,
a wrap command is available for building and installing packages~\cite{wrappr}, optionally enabling sandboxing.
Nevertheless, a breach of the central server enables an attacker to modify packages arbitrarily.
Relying only on TLS for packages is suboptimal, because many TLS implementations suffer from a long history of security vulnerabilities (e.g. goto fail).

@@

% LG: What about injecting packages (dependencies) into the user system ? I have
% \texttt{provides:} in mind, that may enable this without changing the contents
% of a package

@@

Each author updates their own packages, which should be free of conflicts due to separate resources for each package.
% unclear without VC in mind, which is'nt introduced yet: precise ``conflicts between concurrent repository updates'' ?
If a conflict is detected, it is up to the janitors to decide which update should go through, and which should be resubmitted on top of the other.

@@

The \texttt{keys} directory contains one file for each author and janitor, named after the key identifier.
The \texttt{sigs} directory contains one file for each janitor, named after the janitor key identifier.
The \texttt{data} directory consists of subdirectories, which each must contain a file \texttt{authorisation} and a file \texttt{releases}, plus possibly any subdirectories.
Each subdirectory must be listed in the \texttt{releases} file, and must contain a \texttt{checksum} file besides any other data files and directories (all listed in the checksum file).

@@

Package metadata, signatures, and public keys are distributed in the same repository to prevent attackers from hindering one communication link, e.g. the public key one.
This would otherwise allow a detected attacker who compromised a key to deliver metadata signed with this compromised key.
% LG: I am not sure I really get your meaning here
